---
title: "Getting Started with binomial"
author: "Sean Hanley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Combinatorics

The package `"binomial"` allows  the user to play around with simple binomial theorem functions and basic plots.

## Using `binomial`

Here's how to use the available functions, starting with `bin_choose()`, which Calculates the number of combinations in which k successes occur in n trials:

```{r}
bin_choose(5, 0)
bin_choose(5, 1:3)
```

`bin_probability()` finds probable number of successes:

```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
```

`bin_distribution()` finds the probability distribution:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```
`bin_cumulative()` finds the cumulative probability that sums to 1:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
#shows a graph of distribution
```
`bin_variable()` creates an object of class "binvar" then display a summary:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```
`bin_mean()` calculate the mean of binomial distribution(np):
```{r}
bin_mean(10, 0.3)
```
`bin_variance` calculate variance of binomial dist. (np(1-p)):
```{r}
bin_variance(10, 0.3)
```
`bin_mode()` calculate the most likely number of successes in n independent trials. (the floor of np + p):
```{r}
bin_mode(10, 0.3)
```
`bin_skewness()` calculate asymmetry of the probability dist. of a random variable about its mean.:
```{r}
bin_skewness(10, 0.3)
```
`bin_kurtosis()`calculate measure of "tailedness" of probability dist. of a random variable:
```{r}
bin_kurtosis(10, 0.3)
```

